Interactive Filter and Display of Hillary Clinton's Emails: \\A Cautionary Tale of Metadata

### 2017-04-03 VAST_submission/vgtc_journal_latex/paper.tex
Added Wikileaks transcription error on b9

 We need to also point out that the extraction of data is always an opportunity for error to occur.   For example, we have already mentioned difficulties with processing email addresses that have been partially or entirely redacted.  There are no doubt other errors as well.

 The process we have followed is an automated one.  One conducted by hand, by examining each pdf, would likely produce better data but not necessarily for more than 30,000 records.

>>>>

 We need to also point out that the extraction of data is always an opportunity for error to occur.   For example, we have already mentioned difficulties with processing email addresses that have been partially or entirely redacted.  The Wikileaks transcription from pdf to HTML is also imperfect.  For example, the string ``b9''  appears in one email record (Doc ID: 10257) in the Wikileaks transcription\cite{errorWikileaks} as a transcription error of the day ``09'' from the original pdf.  This might be grabbed as a B9  redaction code, if one is not careful.  The same email record also has ``To'' and ``From'' header which is empty except for a date.  This header does not appear in the original pdf; rather the pdf begins with the next one inside the HTML.   There are no doubt other errors as well.

 The process we have followed is an automated one.  One conducted by hand, by examining each pdf, would likely produce better data but not necessarily for more than 30,000 records.  At least a check by hand of all HTML email records with blank to and froms at the beginning could be of some value.
